---
title: 'Week 7 : HW01: 5 Chart Diamond'
author: "Suvichuk Klao"
date: "2023-10-19"
output:
  pdf_document: default
  html_document: default
---

# Instruction
Use diamonds dataset to create 5 chart. Knit pdf and submit in discord
```{R}
library(tidyverse)
```

## 1st chart

```{R}
set.seed(62)
small_diamonds <- sample_n(diamonds, 5000)
ggplot(small_diamonds, aes(price,carat))+
  geom_point(aes(col= cut))+
  geom_smooth()+
  facet_wrap(~color, ncol= 3)+
  theme_minimal()+
  labs(title = "the best price and carat for buying by color",
       y = "carat",
       x = "price USD")

```
### 1. Scatter plot x = price, y = carat -> the best price and carat is 0-$5000 and 0.01-1 carat

## 2nd chart

```{R}
ndiamonds <- diamonds%>%
  filter(table >=50 & table < 70)

ggplot(ndiamonds, aes(table,carat))+
  geom_point(aes(col= cut))+
  geom_smooth()+
  facet_wrap(~cut, ncol= 3)+
  theme_minimal()+
  labs(title = "Relationship table and carat by cut",
       x = "width of top of diamond",
       y = "carat")
```
### 2. Scatter plot x = table, y = carat -> the table isn't affect to the size of carat but affect to the cut

## 3rd chart

```{r}
set.seed(62)
small_diamonds <- sample_n(diamonds, 5000)
ggplot(small_diamonds, aes(cut,table, col = cut))+
  geom_boxplot()+
  theme_minimal()+
  labs(title = "Relationship cut and table by color",
  x = "cut",
  y = "width of top of diamond")
```
### 3. boxplot x = table, y = cut -> the table isn't affect to the type of cut

## 4th chart

```{r}
set.seed(62)
small_diamonds <- sample_n(diamonds, 5000)
SMN <-small_diamonds%>%
    group_by(clarity)%>%
    summarise( QTY =n())


ggplot(SMN, aes(x = clarity, y = QTY, fill = clarity)) +
  geom_bar(stat = "identity") +
  theme_minimal()+
  labs(title = "Count QTY of clarity",
       x = "clarity",
       y = "QTY")
```
### 4. Histogram x = clasity -> The most QTY of clarity is SI1

## 5th chart

```{r}
set.seed(62)
small_diamonds <- diamonds%>%
  sample_n(5000)%>%
  filter(x > 1)


ggplot(small_diamonds, aes(x,price, col=color))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~color, ncol= 3)+
  theme_minimal()+
  labs(title = "The lenght diamond is affect to price or not ",
       x = "lenght in mm",
       y = "price USD")
```
### 5. Sccatter plot x = x, y= price -> Yes, it is affect when the lenght is more than 6mm the price will extremly hight 

## Source: Diamonds from ggplots2 package
